### 2014-11-12 tex/intro.tex
precision

The heap summary approach for symbolic execution is sound and complete
with respect to anything you can prove using a GSE machine. We should
the existence of a bi-simulation relation. In other words, any
property that can be proved using GSE can also be proved using heap
summaries, furthermore, any property proved by heap summaries can also
be proved by GSE---given the same bounds on heap reference chains and
loops.

>>>>

The heap summary approach for symbolic execution is sound and complete
with respect to a GSE machine. We show the existence of a
bi-simulation relation. In other words, any property that can be
proved using GSE can also be proved using heap summaries, furthermore,
any property proved by heap summaries can also be proved by
GSE---given the same bounds on heap reference chains and loops.
